\chapter{Log}

\section{Handling Locals (2017-09-13)}

\textbf{Problem:} \verb`MemberExpr` does not mean what's being referenced is a
field.
For instance consider the following examples:

\begin{verbatim}
bool emptyField() const {
  return f.empty();
}
\end{verbatim}

\begin{verbatim}
bool emptyLocal() const {
  std::vector<int> l;
  return l.empty();
}
\end{verbatim}

Even if you can assume \verb`empty` may mutate, the local version should not
flag that the object may mutate.
Instead of \verb`MemberExpr` just returning that a value could be a field, I
should check its \verb`getBase` and possibly \verb`getMemberDecl` (although the
latter may only be good for checking the \const{} qualifier on method calls).
If \verb`getBase` is a \verb`CXXThisExpr` then it's part of the object, if it's
a \verb`VarDecl` then it's a local.
Note that \verb`VarDecl` has a \verb`hasLocalStorage` function that I should be
using.

Actually, I shouldn't have to specifically handle locals.
I just need to handle my detection a lot better.
I re-organized the code to better handle every case.

\section{Handling Locals without MemberExpr (2017-09-14)}

I need to better distinguish between changes to an actual field and something
that just previously had a field value.
An instance of each is:

\begin{verbatim}
void modField() const {
  f = 4;
}
\end{verbatim}

\begin{verbatim}
void modLocal() const {
  int x = f;
  x = 4;
}
\end{verbatim}

Note also that:

\begin{verbatim}
void foo() const {
  *f, *g = 4;
}
\end{verbatim}

The expression \verb`*f` is unused.
There will be no writes through a dereferenced \verb`f`.

\section{Visitors}

\textbf{\ttfamily Exprs.cpp} - LHSVisitor

\textbf{\ttfamily Methods.cpp} - ResultVisitor

\textbf{\ttfamily ValuesMaybleField.cpp} -  MaybeFieldsVisitor

\textbf{\ttfamily ValuesMustLiteral.cpp} - MustLiteralsVisitor

\textbf{\ttfamily VariableKinds.cpp} - TransferFunction
